ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-11-07 proposal.tex
Updated labNotebook.tex and proposal.tex
Added entries for 11/2 and 11/4 and created blank entry for 11/9

Added subsections Design and Simulation Results
Updated proposal.tex
Added figures for the estimated transfer function models of the steering system
Updated proposal.tex

\usepackage{siunitx}
\sisetup{unitsep=\cdot}

@@

\begin{minipage}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=3in]{figs/inkscape/steeringModelArchitecture}
    \caption{Block Diagram of the Vehicle Steering Model.}
    \label{fig:steerBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Block Diagram of the Vehicle Brake Model.}
    \label{fig:brakeBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
    \caption{Block Diagram of the Vehicle Acceleration Model.}
    \label{fig:accelBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/inkscape/shiftModelArchitecture}
    \caption{Block Diagram of the Vehicle Shift Model.}
    \label{fig:shiftBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/inkscape/speedControlModelArchitecture}
    \caption{Block Diagram of the Vehicle Speed Control Model.}
    \label{fig:cruiseBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/inkscape/speedModelArchitecture}
    \caption{Block Diagram of the Vehicle Speed Model.}
    \label{fig:speedBlockDiag}
\end{minipage}

@@

% % \subsection{Simulation Results} \label{sec:simresults}

% % \subsection{Design} \label{sec:design}

% % \subsection{Experimental Activities} \label{sec:expresults}

>>>>

\usepackage{siunitx}

@@

\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=3in]{figs/inkscape/steeringModelArchitecture}
    \caption{Block Diagram of the Vehicle Steering Model.}
    \label{fig:steerBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Block Diagram of the Vehicle Brake Model.}
    \label{fig:brakeBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
    \caption{Block Diagram of the Vehicle Acceleration Model.}
    \label{fig:accelBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/inkscape/shiftModelArchitecture}
    \caption{Block Diagram of the Vehicle Shift Model.}
    \label{fig:shiftBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/inkscape/speedControlModelArchitecture}
    \caption{Block Diagram of the Vehicle Speed Control Model.}
    \label{fig:cruiseBlockDiag}
\end{figure}
%
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/inkscape/speedModelArchitecture}
    \caption{Block Diagram of the Vehicle Speed Model.}
    \label{fig:speedBlockDiag}
\end{figure}

@@

\subsection{Design} \label{sec:design}
Each subsystem that we are modeling are set up in a similar manner. In manual mode, the torque voltages that control each subsystem are sent by the electronic control unit (ECU). In order to control the vehicle autonomously, the vehicle subsystem switches to by-wire mode. In by-wire mode, the torque voltages from the ECU are discarded by open-circuiting the motors that control each subsystem. Instead, controllers built by AutonomouStuff send the torque voltages to the motor using relays.

\subsection{Simulation Results} \label{sec:simresults}
In \autoref{fig:byWireSteerModel}, the output steering angle is plotted versus time when the vehicle is in by-wire mode. The figure shows the output steering angle from some data collected to depict the steering system behavior plotted with the behavior of the estimated model. The best fit percentage for this model is 85.54. Likewise, \autoref{fig:manualSteerModel} depicts the output steering angle plotted versus time when the vehicle is in manual mode. The best fit percentage for this model is 90.27.

\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/img/byWireSteeringTransferFunctionModel}
    \caption{Output of Estimated By-Wire System Model}
    \label{fig:byWireSteerModel}
\end{figure}
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=2in]{figs/img/manualSteeringTransferFunctionModel}
    \caption{Output of Estimated Manual System Model}
    \label{fig:manualSteerModel}
\end{figure}
